Figures

### 2021-03-04 inst/manuscript/figures.Rmd
Edits to Discussion nearly complete

p1 <- ggplot(africa) + 
  geom_sf(fill = "gray97", color = "grey", size = 0.25) +
  geom_sf(data = aois, fill = "grey85", col = "black", size = 0.3) +
  geom_sf(data = train_val_q, aes(color = Cluster, fill = Cluster), 
          size = 0.05) +   
  scale_color_manual(values = pal) +
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) +
  guides(colour = guide_legend(override.aes = list(size = 1, fill = NA))) + 
  theme_void() + 
  theme(legend.key = element_rect(fill = "grey85", color = "transparent"))

pal <- c(RColorBrewer::brewer.pal(n = 4, "Spectral"), "white")
p2 <- ggplot(africa) + geom_sf(fill = "gray97", color = "grey", size = 0.25) +
  geom_sf(data = aois, fill = "grey85", col = "black", size = 0.3) + 
  geom_sf(data = train_val_sites$active, aes(color = Type), size = 0.05) +
  scale_color_manual(values = pal) +
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) +
  guides(colour = guide_legend(override.aes = list(size = 1, fill = NA))) + 
  theme_void() + 
  theme(legend.key = element_rect(fill = "grey85", color = "transparent"))

>>>>

p1 <- ggplot(africa) + 
  geom_sf(fill = "gray97", color = "grey", size = 0.25) +
  geom_sf(data = aois, fill = "grey85", col = "black", size = 0.3) +
  geom_sf(data = train_val_q, aes(color = Cluster, fill = Cluster), 
          size = 0.05) +   
  geom_sf_text(data = st_centroid(aez) %>% filter(ID != 8) %>% arrange(ID),
               aes(label = ID), 
               nudge_x = c(0.75, 0, 0, -1.25, -1, -1.25, 0),
               nudge_y = c(0.25, 0, 0, 0.7, 0.25, 1, 0),
               size = 3, col = "grey60") + 
  geom_sf(data = aez, fill = "transparent", color = "gray60", size = 0.25) +
  scale_color_manual(values = pal) +
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) +
  guides(colour = guide_legend(override.aes = list(size = 1, fill = NA))) + 
  theme_void() + 
  theme(legend.key = element_rect(fill = "grey85", color = "transparent"))

pal <- c(RColorBrewer::brewer.pal(n = 4, "Spectral"), "white")
p2 <- ggplot(africa) + geom_sf(fill = "gray97", color = "grey", size = 0.25) +
  geom_sf(data = aois, fill = "grey85", col = "black", size = 0.3) +
  geom_sf(data = train_val_sites$active, aes(color = Type), size = 0.05) +
  geom_sf_text(data = st_centroid(aez) %>% filter(ID != 8) %>% arrange(ID),
               aes(label = ID), 
               nudge_x = c(0.75, 0, 0, -1.25, -1, -1.25, 0),
               nudge_y = c(0.25, 0, 0, 0.7, 0.25, 1, 0),
               size = 3, col = "grey60") + 
  geom_sf(data = aez, fill = "transparent", color = "gray60", size = 0.25) +
  scale_color_manual(values = pal) +
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) +
  guides(colour = guide_legend(override.aes = list(size = 1, fill = NA))) + 
  theme_void() + 
  theme(legend.key = element_rect(fill = "grey85", color = "transparent"))
